---
title: "p8105_hw1_hz2771"
author: 'Haolin Zhong (UNI: hz2771)'
date: "2021/9/28"
output: github_document
---


```{r, message=FALSE}
library(tidyverse)
library(tibble)
library(ggplot2)
```


# Problem 1

## Create the dataframe

```{r}
example_df = tibble(
  random_samples = rnorm(10),
  sample_gt_0 = random_samples > 0,
  chs = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  fct = factor(c("low", "low", "low", "mid", "mid", "mid",  "mid", "high", "high","high"), levels = c("low", "mid", "high"))
)
```


## Take the mean of each variable

```{r}
mean(pull(example_df, random_samples))
```

- `mean()` works for the column `random_samples`, whose data type is `r class(pull(example_df, random_samples))`.

```{r}
mean(pull(example_df, sample_gt_0))
```

- `mean()` works for the column `sample_gt_0`, whose data type is `r class(pull(example_df, sample_gt_0))`.

```{r}
mean(pull(example_df, chs))
```

- `mean()` doesn't work for the column `chs`, whose data type is `r class(pull(example_df, chs))`.

```{r}
mean(pull(example_df, fct))
```

- `mean()` doesn't work for the column `fct`, whose data type is `r class(pull(example_df, fct))`.





