---
title: "p8105_hw1_hz2771"
author: 'Haolin Zhong (UNI: hz2771)'
date: "2021/9/28"
output: github_document
---

## Import required packages

```{r, message=FALSE}
library(tidyverse)
library(tibble)
library(ggplot2)
```


# Problem 1

## Create the dataframe

```{r}
example_df = tibble(
  random_samples = rnorm(10),
  sample_gt_0 = random_samples > 0,
  chs = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  fct = factor(c("low", "low", "low", "mid", "mid", "mid",  "mid", "high", "high","high"), levels = c("low", "mid", "high"))
)
```


## Take the mean of each variable

```{r, warning = FALSE}
mean(pull(example_df, random_samples))
```

- `mean()` works for the column `random_samples`, whose data type is 
`r class(pull(example_df, random_samples))`.

```{r, warning = FALSE}
mean(pull(example_df, sample_gt_0))
```

- `mean()` works for the column `sample_gt_0`, 
whose data type is `r class(pull(example_df, sample_gt_0))`.

```{r, warning = FALSE}
mean(pull(example_df, chs))
```

- `mean()` doesn't work for the column `chs`, whose data type is 
`r class(pull(example_df, chs))`.

```{r, warning = FALSE}
mean(pull(example_df, fct))
```

- `mean()` doesn't work for the column `fct`, whose data type is 
`r class(pull(example_df, fct))`.


## Try to use as.numeric() to convert logical, character and factor variables

```{r, eval = FALSE}
as.numeric(pull(example_df, sample_gt_0))
as.numeric(pull(example_df, chs))
as.numeric(pull(example_df, fct))
```

- For the logical variable `sample_gt_0`, the output is consist of 0 and 1. 
This is because the logical variable was converted to 1 for `TRUE` and 0 
for `FALSE`. 

- For the character variable `chs`, the output is 10 NA. This is because a 
`character` value couldn't be converted to meaningful `numeric` value in R.

- For the factor variable `fct`, the output is consist of 1, 2, and 3. This is 
because these factor values are ordinal and they were converted to numeric 
values according to their corresponding level (1 for `low`, 2 for `mid`,
3 for `high`).

- This partially helps to explain that why we can use `mean()` on logical 
variables but not character variables. In `mean()`, `TRUE` is also regarded 
as 1 and `FALSE` is regarded as 0. And `mean()` also don't know how to convert 
character variables. The factor variable, although is supported by 
`as.numeric()`, is not supported by `mean()`, because `mean()` only takes 
numeric/logical vectors and date, date-time and time interval objects.


# Problem 2

## Load the peguin dataset

```{r}
data("penguins", package = "palmerpenguins")
```


## Describe the dataset

- This dataset contains `r length(colnames(penguins))` variables, which are: 
`r colnames(penguins)`.

    - `species`: This variable is a `r class(pull(penguins, species))` variable. 
    It contains `r sum(is.na(pull(penguins, species)))` missing value(s). It is
    `r if (!is.ordered(pull(penguins, species))) 'not'` ordinal, and has 
    `r length(levels(pull(penguins, species)))` categories: 
    `r levels(pull(penguins, species))`, which have 
    `r summary(pull(penguins, species)[!is.na(pull(penguins, sex))])` 
    records respectively.
    
    - `island`: This variable is a `r class(pull(penguins, island))` variable. 
    It contains `r sum(is.na(pull(penguins, island)))` missing value(s). It is
    `r if (!is.ordered(pull(penguins, island))) 'not'` ordinal, and has 
    `r length(levels(pull(penguins, island)))` categories: 
    `r levels(pull(penguins, island))`, which have 
    `r summary(pull(penguins, island)[!is.na(pull(penguins, island))])` 
    records respectively.

    - `sex`: This variable is a `r class(pull(penguins, sex))` variable. 
    It contains `r sum(is.na(pull(penguins, sex)))` missing value(s). It is
    `r if (!is.ordered(pull(penguins, sex))) 'not'` ordinal, and has 
    `r length(levels(pull(penguins, sex)))` categories: 
    `r levels(pull(penguins, sex))`, which have 
    `r summary(pull(penguins, sex)[!is.na(pull(penguins, sex))])` 
    records respectively.
    
    - `bill_length_mm`: This variable is a 
    `r class(pull(penguins, bill_length_mm))` variable. It contains 
    `r sum(is.na(pull(penguins, bill_length_mm)))` missing value(s). 
    For this variable, the mean is 
    `r round(mean(pull(penguins, bill_length_mm), na.rm = TRUE), 2)`, 
    the standard deviation is 
    `r round(sd(pull(penguins, bill_length_mm), na.rm = TRUE), 2)`. 
    The 0th,25th, 50th, 75th, 100th percentile values are: 
    `r round(quantile(pull(penguins, bill_length_mm), na.rm = TRUE), 2)`.
    
    - `bill_depth_mm`: This variable is a 
    `r class(pull(penguins, bill_depth_mm))` variable. It contains 
    `r sum(is.na(pull(penguins, bill_depth_mm)))` missing value(s). 
    For this variable, the mean is 
    `r round(mean(pull(penguins, bill_depth_mm), na.rm = TRUE), 2)`, 
    the standard deviation is 
    `r round(sd(pull(penguins, bill_depth_mm), na.rm = TRUE), 2)`. 
    The 0th,25th, 50th, 75th, 100th percentile values are: 
    `r round(quantile(pull(penguins, bill_depth_mm), na.rm = TRUE), 2)`.
    
    - `flipper_length_mm`: This variable is a 
    `r class(pull(penguins, flipper_length_mm))` variable. It contains 
    `r sum(is.na(pull(penguins, flipper_length_mm)))` missing value(s). 
    For this variable, the mean is 
    `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), 2)`, 
    the standard deviation is 
    `r round(sd(pull(penguins, flipper_length_mm), na.rm = TRUE), 2)`. 
    The 0th,25th, 50th, 75th, 100th percentile values are: 
    `r round(quantile(pull(penguins, flipper_length_mm), na.rm = TRUE), 2)`.
    
    - `body_mass_g`: This variable is a 
    `r class(pull(penguins, body_mass_g))` variable. It contains 
    `r sum(is.na(pull(penguins, body_mass_g)))` missing value(s). 
    For this variable, the mean is 
    `r round(mean(pull(penguins, body_mass_g), na.rm = TRUE), 2)`, 
    the standard deviation is 
    `r round(sd(pull(penguins, body_mass_g), na.rm = TRUE), 2)`. 
    The 0th,25th, 50th, 75th, 100th percentile values are: 
    `r round(quantile(pull(penguins, body_mass_g), na.rm = TRUE), 2)`.
    
    - `year`: This variable is a 
    `r class(pull(penguins, year))` variable. It contains 
    `r sum(is.na(pull(penguins, year)))` missing value(s). 
    For this variable, the mean is 
    `r round(mean(pull(penguins, year), na.rm = TRUE), 2)`, 
    the standard deviation is 
    `r round(sd(pull(penguins, year), na.rm = TRUE), 2)`. 
    The 0th,25th, 50th, 75th, 100th percentile values are: 
    `r round(quantile(pull(penguins, year), na.rm = TRUE), 2)`.

- This dataset has `r ncol(penguins)` columns and `r nrow(penguins)` rows.

- The mean flipper length in this dataset is 
`r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), 2)`


## Draw the scatter plot

```{r, warning = FALSE}
figure = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, 
                              color = species)) +
         geom_point()
show(figure)
```

## Save the plot

```{r, warning = FALSE}
ggsave("penguins_bill_flipper.jpg")
```













